Reinforcement Learning Produces Dominant Strategies for the Iterated Prisoner's Dilemma

### 2017-07-08 main.tex
Modify the discussion.
I've changed this slightly based on our discussion.

The Lookerup and Gambler strategies don't do well in Noise so I think
there's something to be said there about the dimensions captured by the
various archetypes.

\subsection{LookerUp}

@@

\subsection{Gambler}

@@

\subsection{Finite State Machines}

@@

The tournament results indicate that pre-trained strategies are generally better
than human designed strategies at maximizing payoff against a diverse set of
opponents. An evolutionary algorithm produces strategies based on multiple
standard machine learning techniques that are able to achieve a higher average
score than any other known opponent in a standard tournament. Most of the trained
strategies use multiple rounds of the history of play (some using all of it) and
outperform memory-one strategies (though the trained memory one strategy performs
well). The generic structure of the trained strategies did not appear to be
critical -- strategies based on lookup tables, finite state machines, and stochastic
variants all performed well. Single layer neural networks also performed well
though these had some aspect of human involvement in the selection of features.
% TODO Question: is this arguably just as much human involvement in the design
% of the lookup tables etc? We could use a lookup table that also picks out the
% action from the middle round, however we have chosen not too.
The success of the other strategy types suggests that a deeper network that
incorporates feature engineering would likely also perform well.

>>>>

\subsection{LookerUp}\label{sec:lookerup}

@@

\subsection{Gambler}\label{sec:gambler}

@@

\subsection{Finite State Machines}\label{sec:fsm}

@@

The tournament results indicate that pre-trained strategies are generally better
than human designed strategies at maximizing payoff against a diverse set of
opponents. An evolutionary algorithm produces strategies based on multiple
standard machine learning techniques that are able to achieve a higher average
score than any other known opponent in a standard tournament. Most of the trained
strategies use multiple rounds of the history of play (some using all of it) and
outperform memory-one strategies (though the trained memory one strategy performs
well). The generic structure of the trained strategies did not appear to be
critical -- strategies based on lookup tables, finite state machines, and stochastic
variants all performed well for standard tournaments.
Single layer neural networks (Section~\ref{sec:ann}) performed well in both
noisy and standard
tournaments
though these had some aspect of human involvement in the selection of features.
This is in line with the other strategies also where human decisions are made
regarding the structure. For the LookerUp and Gambler archetypes
(Sections~\ref{sec:lookerup} and~\ref{sec:gambler})
a decision has to be made
regarding the number of turns of history and initial play that are to be used.
Whilst, the Finite state machines and Hidden Markov models
(Sections\ref{sec:fsm} and~\ref{sec:hmm}) also need input from a
human as to the number of states to use they are much more of a black box and
thus offer wider adaptability.

A lot of strategies could be represented by many archetypes, however some
archetypes will be far more efficient in doing so than
others. The fact that the Lookerup strategy does the best for the standard
tournament indicates that it represents an efficient reduction of
dimension which in turn makes its training more efficient. For the noisy
tournament however the dimension reduction represented by some archetypes
indicates that sufficient features are not captured by the Lookup tables whilst
they are by the
neural network and the finite state machine allowing them to adapt to the noisy
environment.
